% ------------------------------------------------------------------------------------- %
% ODIS Diamond - IDE for D Programming Language                                         %
%                                                                                       %
% This document is a personal essay on IDE specification for D programming language.    %
%                                                                                       %
% Rizo Isrof   <rizo@odis-project.org>                                                  %
% Rui Malheiro  <rui@odis-project.org>                                                  %
% ------------------------------------------------------------------------------------- %

\documentclass[12pt]{article}
\usepackage{fix-cm}

% Project Information ----------------------------------------------------------------- %

% Organization Name
\newcommand{\ProjectOrganization}{ODIS} % Course/class

% Project Name
\newcommand{\ProjectName}{Diamond}

% Publication Title
\newcommand{\PublicationTitle}{Project Planification}

% Project Authors
\newcommand{\PublicationAuthors}{Rizo Isrof, Rui Malheiro}

% Contacts
\newcommand{\Contacts}{\{rizo,rui\}@odis-project.org}

% Project Start Date
\newcommand{\ProjectStartDate}{April,\ 2012}


% Title Page -------------------------------------------------------------------------- %

\title{
	\ProjectOrganization\ --\ \ProjectName \\
	\vspace{10pt}
	\Huge{\textbf{\PublicationTitle}} \\
	\vspace{20pt}
}

\author{
	\Large{\PublicationAuthors}
	\vspace{5pt} \\
	\texttt{\Contacts}
	\vspace{20pt}
}

\date{\textit{\today}}

\begin{document}
\maketitle

% Remove page numbering on the  page.
\thispagestyle{empty}

\clearpage


% Document Content -------------------------------------------------------------------- %

\section{General Tasks}

\begin{itemize}
	\item Create a D/Objective-C compiler.
  	\item Finish the existing DMD Fork by Michel Fortin.
  	\item Extend the LDC.
	\item D-Cocoa Communication
  	\item Communicate with the OS X WindowServer
  	\item Allow the creation of the Cocoa applications in D.
	\item D IDE
	\item D GUI Framework
	\item Declarative language of interfaces with D backend.
	\item Javascript compiler to allow deployment of the application for the Web.
\end{itemize}

\section{Graphical Interface Framework}
In order to provide the native drawing capabilities for the D programming language, the communication with the window system in each platform should be possible. Thus, for the OS X the language must interact with the Cocoa framework, in Linux and BSD systems, the X11 is used and for the Windows - win32 API.

\subsection{GUI Backend for Cocoa}

\begin{itemize}
	\item Make a functional prototype of the D-Cocoa bridge.
	\item Create a minimal text editor with D syntax checking and highlighting.
	\item Make a study of the possible graphical elements that may be integrated into the source code view.
\end{itemize}







\end{document}
